\LaTeXe\ guide for the Journal of Functional Programming

### 2019-05-03 papers/jfp/8-engineering.tex
Make the multiple-output thing clearer
Tweaks to S8

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
data Value = FileNotFound | FileContents ByteString
\end{minted}
\vspace{1mm}

@@

We have given simple implementations assuming a single thread of execution,
but all the build systems we address can actually build independent keys in
parallel. While it complicates the model, the complications can be restricted
exclusively to the scheduler:

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
task :: Partition FilePath -> TasksT Monad Key
task partition (File k) = Just $ TaskT $ \fetch -> do
    let ks = partition k
    let Just i = elemIndex k ks
    vs <- fetch (Files ks)
    pure (vs !! i)
-- patterns matching Files
\end{minted}
\vspace{1mm}

>>>>

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
data Value = FileNotFound | FileContents String
\end{minted}
\vspace{1mm}

@@

We have given simple implementations assuming a single thread of execution,
but all the build systems we address can actually build independent keys in
parallel. While it complicates the model, the complications are restricted
to the scheduler:

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
task :: Partition FilePath -> TasksT Monad Key
task partition (File k) = Just $ TaskT $ \fetch -> do
    let ks = partition k
    let Just i = elemIndex k ks
    vs <- fetch (Files ks)
    pure (vs !! i)
task (Files ["A.hi","A.o"]) = Just $ TaskT $ \fetch ->
    -- run ghc here
-- more rules on elementary subsets as required
\end{minted}
\vspace{1mm}
